A generalization of the Bradley-Terry model for draws in chess

### 2020-10-04 inst/jebo_chess_revision2.tex
minor rephrase

\textcolor{orange}{The maximum likelihood estimate for strengths
  furnishes a natural ranking for the competitors.  \cite{lazear1981}
  observe that such ranking systems occur naturally in organizational
  situations (tournament theory) and the analysis presented here might
  be applicable to this situation, with the advantage of allowing for
  both draws and incumbent advantage.}

>>>>

\textcolor{orange}{The maximum likelihood estimate for strengths
  furnishes a natural ranking for the competitors.  \cite{lazear1981}
  observe that such ranking systems occur naturally in organizational
  situations (tournament theory) and the analysis presented here might
  be applicable to chess, with the advantage of allowing for
  both draws and incumbent advantage.}
